---
title: "Pull stream network associated with a waterbody catchment"
author: "Joseph Stachelek"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pull stream network associated with a waterbody catchment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of this vignette is to demonstrate how to pull the stream network associated with a waterbody catchment. We will use the `extract_network` function to accomplish this task using the built-in `mendota` dataset.

```{r message=FALSE, warning=FALSE}
library(nhdR)
library(dplyr)
library(ggplot2)
library(sf)
```

Let's start by pulling the coordinates associated with Lake Mendota, which will be the largest object (by area) in the waterbody object.

```{r mendota_centroid, warning=FALSE, eval=TRUE}
data(mendota)

largest_waterbody <- which.max(st_area(mendota$sp$NHDWaterbody))
mendota_lake      <- mendota$sp$NHDWaterbody[largest_waterbody, ]
mendota_lake      <- st_transform(mendota_lake, crs = 4326)
mendota_centroid  <- st_coordinates(st_centroid(mendota_lake))
```

Next, we can use the `extract_network` function to pull the stream network associated with Lake Mendota. Notice that we have set the `maxsteps` parameter to **Inf**. If the network is anticipated to be very large it can be a good idea to set this to a discrete (lower) number to avoid returning very large lines objects.

```{r mendota_network, eval=FALSE}
mendota_network <- extract_network(lon = mendota_centroid[1],
  lat = mendota_centroid[2],
  maxsteps = Inf)
```

Finally, we compare the stream network from a geometric buffer around Lake Mendota against the output of `extract_network` to make sure everything is working properly. 

```{r use_precomputed_data, echo=FALSE}
data(mendota_network)
```

```{r mapping}
ggplot() +
  geom_sf(data = mendota$sp$NHDFlowLine) +
  geom_sf(data = mendota_lake, fill = "cyan") +
  geom_sf(data = mendota_network, color = "blue")
```
